---
title: "Introduction to BBOTools"
author: "Mindy Mallory"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package provides tools for working with the Top-of-the-Book (Best Bid-Offer) datasets from the CME Group's [Historical Datamine](http://www.cmegroup.com/market-data/datamine-historical-data.html#topOfBookBbo). These data provide record of every revision to the best bid or best offer. These revisions may have resulted from a new limit order arriving to the market, a limit order being cancelled, or a transaction matching a market order with a limit order or a limit order with another limit order. 

The raw data provided by the CME Group are organized as large fixed-width files. The files are large enough that if one is not careful about memory use, even simple analyses becomes a problem. An extention of R's base data.frame called [data.table](https://github.com/Rdatatable/data.table/wiki) was recently developed by [Matt Dowle](https://github.com/mattdowle) and [Arun Srinivasan](https://github.com/arunsrinivasan) makes working with large datasets in R much more feasible. 

This package utilizes the data.table package extensively. Most of the functions in the BBOTools package are simple wrapper functions the make working with the BBO data more convenient. 

# Installing BBOTools from GitHub


# Importing BBO Data with bboread()



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
